\documentclass{article}
\usepackage{multicol}
\usepackage[utf8]{inputenc}
\usepackage[textwidth=460pt, voffset=0pt]{geometry}
\usepackage{fancyhdr}
\begin{document}
\title{\vspace{-5ex}Crop Allocation}
\author{\vspace{-5ex}}
\date{\vspace{-5ex}}
\pagestyle{fancy}
\fancyhf{}
\lhead{ACIO 2023 Contest 2.5}
\rfoot{Page \thepage}

\begin{center}
\huge{Crop Allocation}\small\\
\vspace{5ex}
\begin{tabular}{|c|c|} 
\hline
Time Limit & Memory Limit \\
\hline
1 second & 128 MB \\

\hline
\end{tabular}
\end{center}
\section*{Statement}

As a well-respected member of the Agricultural Computational Insights Organization (ACIO), you have
been tasked to the following job: You are given a linear piece of land split into $N$ cells, where each cell
can contain at most one crop. Each cell also has a soil quality value $a_i$, which can be positive, negative or
zero.

You have $Q$ different plans. In the $j$th such plan, you have $k_j$ different types of crops which you can plant onto the land, but for each type of
crop, they must occupy in a contiguous set of cells to keep maintenance costs down. There are an infinite amount of crops of each type.

Your task is, for each plan, to find the maximum possible sum of the soil
quality value where the crops are planted. You do not need to plant all $k_j$ types of crops, or even any
crops at all.

\section*{Input}

\begin{itemize}
\item The first line of input contains the integers $N$ and $Q$.
\item The next line of input contains the space-separated integers $a_1, \dots, a_N$.
\item The next line of input contains the space-separated integers $k_1, \dots, k_Q$.
\end{itemize}

\section*{Output}

Output $Q$ lines, the $i$th of which is the answer for the $i$th plan.

\begin{multicols}{2}
\section*{Sample Input 1}
{\tt
5 1\\
5 -2 3 -3 5\\
2
}
\columnbreak
\section*{Sample Input 2}
{\tt
6 4\\
-1 3 4 -4 3 2\\
1 2 3 6
}
\end{multicols}
\begin{multicols}{2}
\section*{Sample Output 1}
{\tt
11\\
\\
\\
}
\columnbreak
\section*{Sample Output 2}
{\tt
8\\
12\\
12\\
12
}
\end{multicols}

\newpage
\section*{Constraints}
\begin{itemize}
\item $1 \le N, Q \le 10^5$
\item $-10^4 \le a_i \le 10^4$
\item $1 \le k_j \le N$
\item All $k_j$ are unique and in ascending order.
\end{itemize}

\section*{Subtasks}
\begin{tabular}{l*{6}{c}r}
Number & Points & $N$ & $Q$ & $k_j$\\
\hline
1 & 8 & $N \le 10^5$ & $Q = 1$ & $k_j = 1$ \\
2 & 15 & $N \le 10^5$ & $Q = 1$ & $k_j \le 2$ \\
3 & 27 & $N \le 10^5$ & $Q = 1$ & $k_j \le 50$ \\
4 & 23 & $N \le 10^5$ & $Q = 1$ & $k_j \le N$ \\
5 & 27 & $N \le 10^5$ & $Q \le 10^5$ & $k_j \le N$
\end{tabular}
\end{document}
